---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
library(data.table)
```
# qubitr

Analyse results from the Clariostar Qubit assay

## Installation

You can use `devtools` to install qubitr from GitHub:

``` r
install.packages("devtools")
devtools::install_github("TomHarrop/qubitr")
```

## Example

#### Load `qubitr` and `data.table`

```{r example}
library(data.table)
library(qubitr)
```

#### Load the raw data

- You'll need columns called `plate_row`, `plate_col` and  `raw_fl` for the analysis. `content` helps you find the blank and standard wells.

```{r example2}
my_col_names <- c("plate_row",
                  "plate_col",
                  "content",
                  "raw_fl")
```

- This command will be different for different input files, especially the `skip` argument.

```{r example3}
raw_data <- fread("my_clariostar_data.csv",
                  skip = 11,
                  select = c(1:4),
                  col.names = my_col_names)
head(raw_data)
```

#### Add volumes

- Note that `AddVolumes()` modifies `raw_data`, rather than returning a new `data.table` (*i.e.* it has **side effects**)

```{r example5}
AddVolumes(raw_data, "A1", "D5", 1, 50)
AddVolumes(raw_data, "A6", "H6", 1, 50)
AddVolumes(raw_data, "A7", "H11", 10, 800)
AddVolumes(raw_data, "E5", "H5", 10, 800)
```

#### Subtract background

- Find the blank wells and the standard wells

```{r example4}
raw_data[grep("^Standard", content)]
raw_data[grep("^Blank", content)]
```

- Subtract the mean of the `blank_wells` from the `raw_fl` column

```{r example6}
background_subtracted <- SubtractBackground(raw_data, c("A12", "B12"))
```

#### Run the linear model

- specify the standard wells and the amount of DNA added to them

```{r example7}
standard_wells <- data.table(well = paste0(LETTERS[3:8], 12),
                             amount = c(rep(10, 3), rep(100, 3)))
standard_wells
```

- calculate the amounts in the unknown wells

```{r example7a}
calculated_amounts <- CalculateAmounts(background_subtracted, standard_wells)
```

- extract the original sample amounts from the results of `CalculateAmounts()`

```{r example8}
final_results <- ExtractResults(calculated_amounts)
head(final_results)
```

